Mermaid with R + consort

### 2023-07-25 Misc/Visuals_Interactives/mermaid_consort.qmd
Major Style Changes - and improved experimental design figure.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

```{mermaid}
%%| fig-cap: "Mean Vx over training blocks"

flowchart LR
    data1(Varied Training<br/>800-1000<br/>1000-1200<br/>1200-1400)
    data2(Constant Training<br/>800-1000)
    Test1(Testing - No Feedback<br/>100-300<br/>350-550<br/>600-800)
    Test2(Test From Train<br/>800-1000<br/>1000-1200<br/>1200-1400)
    Test3(Testing - Feedback<br/>100-300<br/>350-550<br/>600-800)

    data1 --> Test1
    data2 --> Test1
    Test1 --> Test2
    Test2 --> Test3

%% https://quarto.org/docs/authoring/diagrams.html
```

```{dot}
//| label: fig-simple
//| fig-cap: "This is a simple graphviz graph."
//| fig-width: 7.5
//| fig-responsive: false
digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled, fillcolor = Linen]

  data1 [label = "Varied Training\n800-1000\n1000-1200\n1200-1400"]
  data2 [label = "Constant Training\n800-1000"]
  Test1 [label = "Testing - No Feedback\n100-300\n350-550\n600-800"]
  Test2 [label = "Test From Train\n800-1000\n1000-1200\n1200-1400"]
  Test3 [label = "Testing - Feedback\n100-300\n350-550\n600-800"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1
  Test1 -> Test2
  Test2 -> Test3
}
```

```{dot}
//| label: fig-simple2
//| fig-cap: "This is a simple graphviz graph."
//| fig-width: 7.5
//| fig-height: 2.5

digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled, fillcolor = Linen]

  data1 [label = "Varied Training\n800-1000\n1000-1200\n1200-1400"]
  data2 [label = "Constant Training\n800-1000"]
  Test1 [label = "Testing - No Feedback\n100-300\n350-550\n600-800"]
  Test2 [label = "Test From Train\n800-1000\n1000-1200\n1200-1400"]
  Test3 [label = "Testing - Feedback\n100-300\n350-550\n600-800"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1
  Test1 -> Test2 [dir=both, constraint= false]
  Test2 -> Test3
}

## subgraph
```{dot}

digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled, fillcolor = Linen]

  data1 [label = "Varied Training\n800-1000\n1000-1200\n1200-1400"]
  data2 [label = "Constant Training\n800-1000"]
  Test1 [label = "Testing - No Feedback\n100-300\n350-550\n600-800"]
  Test2 [label = "Test From Train\n800-1000\n1000-1200\n1200-1400"]
  Test3 [label = "Testing - Feedback\n100-300\n350-550\n600-800"]

  // edge definitions with the node IDs
  data1 -> subgraph1
  data2 -> subgraph1

  subgraph cluster_counterbalanced {
    label = "Counterbalanced Order"
    Test1
    Test2
  }

  subgraph1 -> Test3
}

digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled, fillcolor = Linen]

  data1 [label = "Varied Training\n800-1000\n1000-1200\n1200-1400"]
  data2 [label = "Constant Training\n800-1000"]
  Test3 [label = "Testing - Feedback\n100-300\n350-550\n600-800"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1

  subgraph cluster {
    label = "Counterbalanced Order"
    Test1 [label = "Testing - No Feedback\n100-300\n350-550\n600-800"]
    Test2 [label = "Test From Train\n800-1000\n1000-1200\n1200-1400"]
    Test1 -> Test2
  }

  Test2 -> Test3
}
```

```{dot}
digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled]

  data1 [label = "Varied Training\n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
  data2 [label = "Constant Training\n800-1000", fillcolor = "#00A08A"]
  Test3 [label = "Testing - Feedback\n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1

  subgraph cluster {
    label = "Counterbalanced Order"
    Test1 [label = "Testing - No Feedback\n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test2 [label = "Test From Train\n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }

  Test2 -> Test3
}

@@

test

@@

test2

@@

test3

@@

test4

@@

test5

@@

test6

@@

test7

@@

test8

@@

htab

@@

mermaid maker

@@

node plot
